\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\title{\textbf{Milestone 2: Agentic AI Research Assistant}}
\author{Autonomous AI Engineer}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This report details the implementation of Milestone 2, which extends a traditional NLP system into an advanced Agentic AI Research Assistant. Utilizing LangGraph for multi-agent orchestration, the system performs autonomous web searching, content retrieval, reasoning, and validation to generate high-quality research reports.
\end{abstract}

\section{Introduction}
The objective of Milestone 2 was to transition from a classical NLP pipeline to an intelligent, agent-based autonomous system. The assistant is designed to handle open-ended research queries by scouring the web, synthesizing information, and ensuring factual consistency through a series of specialized nodes.

\section{System Architecture}
The core of the system is built on a \textbf{StateGraph} using LangGraph. The graph manages the flow of information through several key nodes:

\begin{itemize}
    \item \textbf{Search Node}: Leverages the Tavily API to identify the most relevant academic and web sources.
    \item \textbf{Retrieve Node}: Scrapes and cleans text content from the identified URLs.
    \item \textbf{Summarize Node}: Uses Large Language Models (LLMs) to condense document segments.
    \item \textbf{Reason Node}: Synthesizes summaries into cohesive insights and findings.
    \item \textbf{Validate Node}: Detects contradictions, uncertainties, or gaps in the synthesized data.
    \item \textbf{Report Node}: Formats the final results into a structured JSON and Markdown report.
\end{itemize}

\section{Technical Implementation}

\subsection{Backend}
The backend is implemented using \textbf{FastAPI} and integrates \textbf{LangChain} for model interactions. Environment variables are used to securely manage API keys for Tavily and OpenAI/Groq.

\subsection{Frontend}
The user interface is a premium \textbf{React} application built with \textbf{Vite}. It features a modern dark-themed aesthetic with glassmorphism components and real-time state feedback.

\subsection{PDF Export}
A custom PDF generation utility was implemented using the \texttt{fpdf2} library, allowing users to download a formal version of the generated research reports.

\section{Deployment}
The system is architected for cloud deployment:
\begin{itemize}
    \item \textbf{Backend}: Deployed on Render using a blueprint configuration (\texttt{render.yaml}).
    \item \textbf{Frontend}: Deployed on Vercel with optimized static build settings (\texttt{vercel.json}).
\end{itemize}

\section{Conclusion}
Milestone 2 successfully demonstrates the power of agentic workflows in automating complex research tasks. By combining structured state management with autonomous reasoning, the system provides a significant leap forward in AI-assisted information synthesis.

\end{document}
